---
title: "Serum Analysis"
output: html_notebook
by: Khadijat I.
---

#Introduction

This is an analysis based on serum sample taken to analyze the level of **enzymes** present in the serum in comparison with the level of **protein** in the serum.
The *enzymes* present include:
*catalase
*GSH
*GPX
*MDA

First, the packages are loaded.

```{r}
library(tidyverse)
```

The raw data is imported and viewed.

```{}
serum_part <- read_excel("serum_part.xlsx")
View(serum_part)
```

#Analysis

##Data Summary

```{r}
serum_summary <-
  serum_part %>%
  rename(protein = "Total protein") %>%
  summarise(mean(protein), sd(protein), mean(catalase), sd(catalase),
            mean(GPX), sd(GPX), mean(MDA), sd(MDA), mean(GSH), sd(GSH),
            cor(protein, catalase, method = "pearson"),
            cor(protein, GSH, method = "pearson"),
            cor(protein, MDA, method = "pearson"),
            cor(protein, GPX, method = "pearson"))
```

view summary

```{r}
head(serum_summary)
View(serum_summary)
```

##Data Cleaning

For consistency, "Total protein" column is renamed to "protein".

```{r}
serum_part1 <- rename(serum_part, protein = `Total protein`)
head(serum_part1)
```

##Linear Regression

###Protein vs. Catalase
```{r}
plot(serum_part1$protein, serum_part1$catalase)
abline(lm(serum_part1$protein~serum_part1$catalase))
```

###Protein vs. GSH
```{r}
plot(serum_part1$protein, serum_part1$GSH)
abline(lm(serum_part1$protein~serum_part1$GSH))
```

###Protein vs. GPX
```{r}
plot(serum_part1$protein, serum_part1$GPX)
abline(lm(serum_part1$protein~serum_part1$GPX))
```

###Protein vs. MDA
```{r}
plot(serum_part1$protein, serum_part1$MDA)
abline(lm(serum_part1$protein~serum_part1$MDA))
```
